---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ryelp

The goal of ryelp is to ... *MAYBE CALL [YELP FUSION API V3](https://www.yelp.ca/developers)*? In the meantime, check out the brute force example below. Created just to get a STAT 545 student unstuck.

## Installation

You can install ryelp from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jennybc/ryelp")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

## Brute force

Example of working with [Yelp Fusion API](https://www.yelp.ca/developers) from first principles (vs really exploiting [httr](https://github.com/hadley/httr)).

```{r}
library(httr)
library(purrr)

res <- POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
                        client_id = Sys.getenv("YELP_ID"),
                        client_secret = Sys.getenv("YELP_SECRET")))
token <- content(res)$access_token

yelp <- "https://api.yelp.com"
term <- "coffee"
location <- "Vancouver, BC"
limit <- 3
(url <-
    modify_url(yelp, path = c("v3", "businesses", "search"),
               query = list(term = term, location = location, limit = limit)))
res <- GET(url, add_headers('Authorization' = paste("bearer", token)))
http_status(res)
ct <- content(res)
ct$businesses %>% 
  map_df(`[`, c("name", "phone"))
```

